{{< var titll >}}

### 2024-07-19 presentation.qmd
befrem

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
modlat <- eqpar$meql
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
# abc <- seloutput(selreport(appsn))
# abc <- seloutput(selreport(apprn))
```

@@

::: {.column width="50%"}
Non-rigged election
```{r}
#appsn[[4]]
```

@@

Rigged election using standard form
```{r}
#apprs[[4]]
```

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r #paste0(round(penf,3))`$
\end{equation*}

Election outome 
  - Integral `r #round(polynom::integral(penf,c(0,1)),3)`
  - Counting `r #round(rppnf[[1]]$desms[7,2],3)`

@@

\begin{equation*}
f(x)_{0}^{1}=`r #paste0(round(per1,3))`$
\end{equation*}

Election outome
```{r, echo=F}
#round(polynom::integral(per1,c(0,1)),3)
```

>>>>

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
library(polynom)
modlat <- eqpar$meql
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
ssr <- selreport(ManifoldDestiny::appsn)
rsr  <- selreport(ManifoldDestiny::apprn)
```

@@

::: {.column width="50%"}
Non-rigged election
```{r}
ssr[[1]]$pl_2dsort
```

@@

Rigged election using standard form
```{r}
rsr[[1]]$pl_2dsort
```

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r round(polynomial(unname(rsr[[1]]$polyc[[1]]$coefficients)))`
\end{equation*}

Election outome 
  - Integral `r round(polynom::integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients)),c(0,1),3),3)`
  - Counting `r round(ssr[[1]]$desms[7,2],3)`

```{r}
knitr::knit_exit()
```

@@

\begin{equation*}
$f(x)_{0}^{1}=`r round(polynomial(unname(rsr[[1]]$polyc[[1]]$coefficients)))`$
\end{equation*}

Election outome
```{r, echo=F}
round(polynom::integral(polynomial(unname(rsr[[1]]$polyc[[1]]$coefficients)),c(0,1),3),3)
```
